Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-01-31 TACAS2018/paper.tex

Using the described technique we managed to synthesize controllers for $509$ benchmarks (compared to $290$ found by our baseline), with a median synthesis time of $16.8$ seconds.
%and the maximum observed synthesis time was under 10 minutes for a $4^{th}$ order system ($8^{th}$ order considering the observer).
We consider these times short enough to be of practical use to control engineers.
There are cases for which the system fails to find a controller.  We use a
relatively short timeout, so it is possible that longer timeouts would instead lead to a
valid solution. However, as stated before, the solution is sound but incomplete,
so it is impossible to tell if a solution exists in these cases.

In order to show the improvements due to our optimization-enhanced CEGIS, we
compared our approach against a standard CEGIS procedure.  For the majority of
our benchmarks, we observe that our approach is significantly faster than
standard CEGIS. We further note that the number of times standard CEGIS times
out is much larger than CEGIS-OR which results in more found solutions by the latter.
The magnitude of the improvement is however, largely dependent on the shape of the problem.

@@

This largest improvement however, is due to the elimination of counterexamples that would have been
created without the refinement. Since further synthesis require increasingly
complex models which are linear in the number of multiplications, eliminating 
these results in large improvements.  In cases when the initial candidate is
suitable, we gain nothing with the refinement and therefore find similar times.
Improvements using this approach will therefore be observed when the safety
specification is tight and the original loop would require multiple counterexamples.

>>>>

Using the described technique we managed to synthesize controllers for $509$ benchmarks (compared to $290$ found by our baseline), with a median synthesis time of $16.8$ seconds.
%and the maximum observed synthesis time was under 10 minutes for a $4^{th}$ order system ($8^{th}$ order considering the observer).
We consider these times short enough to be of practical use to control engineers.
There are cases for which the system fails to find a controller.  We use a
relatively short timeout, so it is possible that longer timeouts would instead lead to a
valid solution. However, as stated before, the solution is sound but incomplete,
so it is impossible to tell if a solution exists in these cases. 
\note{I don't think this is stated before so explain it here.}

In order to show the improvements due to our optimization-enhanced CEGIS, we
compared our approach against a standard CEGIS procedure.  For the majority of
our benchmarks, we observe that our approach is significantly faster than
standard CEGIS. We further note that the number of times standard CEGIS times
out is much larger than CEGIS-OR which results in more found solutions.e

%% We observe that the magnitude of the improvement is however, largely dependent on the shape of the problem.

Overall, we observed more improvements with CEGIS-OR for
higher order systems or systems where the safety
specification is tight, meaning that the standard CEGIS loop would require many iterations.
%  We obtain the most improvements for the models with large orders?}
%More interesting cases appear when we increase the order, showing
%% For instance, benchmark X, which timed-out when using standard CEGIS,
%% is running under 2 minutes using CEGIS-OR. This is the result of
%% removing several multiplications which are known to be difficult for
%% SAT solvers \note{I'm not sure readers will relate to where this is happening in the paper. is it the fact that you use that canonical form? then say that. however, i would have thought you do that in
%% both approaches..}.
These improvements are due to the Abstraction Refinement and Optimization in CEGIS-OR.
While abstraction refinement enables us to start with coarse abstractions
that are only refined on demand, 
the optimization
allows to locally improve candidate solutions and avoid entire iterations of the CEGIS loop
(which would have also required more refined abstractions).
%% elimination of counterexamples that
%% would have been created without the refinement. Since further
%% synthesis require increasingly complex models which are linear in the
%% number of multiplications, eliminating these results in large
%% improvements.
While some systems might still require a very pecise
abstraction resulting in many refinements
(this is generally the cause of time-outs in CEGIS-OR),
others allow us to find solutions with rather coarse
abstractions (this is reflected in the smaller minimum
times obtained with CEGIS-OR).

%% Additionally, as abstraction refinement allows us to start with coarse initial
%% abstraction, CEGIS-OR has smaller minimum times than CEGIS, obtained
%% when the initial coarse abstractions were sufficient to synthesise a
%% solution.

%% In cases when the initial candidate is suitable, we
%% gain nothing with the refinement.
%% Overall, we observed more improvements with CEGIS-OR for
%% higher order systems or systems where the safety
%% specification is tight, where the standard CEGIS loop would require many iterations.
%multiple counterexamples.
%% =======
%% out is much larger than CEGIS-OR which results in more found solutions by the latter.
%% The magnitude of the improvement is however, largely dependent on the shape of the problem.

%% This largest improvement however, is due to the elimination of counterexamples that would have been
%% created without the refinement. Since further synthesis require increasingly
%% complex models which are linear in the number of multiplications, eliminating 
%% these results in large improvements.  In cases when the initial candidate is
%% suitable, we gain nothing with the refinement and therefore find similar times.
%% Improvements using this approach will therefore be observed when the safety
%% specification is tight and the original loop would require multiple counterexamples.
%% >>>>>>> 24cc6678b474c2e2bd6bed94342b2d9daca1abee

@@
